---
title: "Multiple_Regression"
output: html_document
---


```{r import_data_all}
library(readr)
library(janitor)
all_features <- read_csv("all_annotations.csv")
mean_df <- read_csv("GoldStandard.csv")
View(all_features)
View(mean_df)
```


----------------------------------------------------------------------------------------------------------------------------------------------------------
-------------------------------------------------------------ASSESS CROSSED RANDOM EFFECTS----------------------------------------------------------------
----------------------------------------------------------------------------------------------------------------------------------------------------------


# We assess wether the crossed random effects (user_IDxSong) are a better fit w.r.t. the individual random intercepts.

```{r lme_Arousal}
library(nlme)
library(lme4)
# Fit linear model with random intercept ID
random.ID.model <- lmer(Arousal ~ (1 |ID), data=all_features) # one random effect
summary(random.ID.model)
# Fit linear model with random intercept song
random.song.model <- lmer(Arousal ~ (1 |Song2), data=all_features) # one random effect
summary(random.song.model)
# Fit linear model with crossed random intercepts ID and Song
crossed.random.model <- lmer(Arousal ~ (1 |Song2) + (1 |ID), data=all_features) # crossed random effects
summary(crossed.random.model)
anova(random.ID.model, random.song.model, crossed.random.model)
```


```{r lme_Valence}
library(nlme)
library(lme4)
# Fit linear model with random intercept ID
random.ID.model <- lmer(Valence ~ (1 |ID), data=all_features) # one random effect
summary(random.ID.model)
# Fit linear model with random intercept song
random.song.model <- lmer(Valence ~ (1 |Song2), data=all_features) # one random effect
summary(random.song.model)
# Fit linear model with crossed random intercepts ID and Song
crossed.random.model <- lmer(Valence ~ (1 |Song2) + (1 |ID), data=all_features) # crossed random effects
summary(crossed.random.model)
anova(random.ID.model, random.song.model, crossed.random.model)
```


----------------------------------------------------------------------------------------------------------------------------------------------------------
-------------------------------------------------------------------FEATURE SELECTION AROUSAL--------------------------------------------------------------
----------------------------------------------------------------------------------------------------------------------------------------------------------


  ##########################################
             GENETIC ALGORITHM  
  ##########################################
 
Initialise predictors search with the feature showing a correlation with the outcome variable (Valence) higher than 0.3

```{r GA_feature_selection_AROUSAL}
library(caret)

set.seed(10)
predictors <- subset(mean_df, select=c(Most_Common_Rhythmic_Value, Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized, Note_Density, pcm_zcr_sma_skewness, Standard_Triads, Melodic_Large_Intervals, Most_Common_Vertical_Interval, Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized, BPM, pcm_intensity_sma_min, Prevalence_of_Dotted_Notes, Importance_of_Bass_Register, Similar_Motion, Second_Strongest_Rhythmic_Pulse, Non.Standard_Chords, F0env_sma_quartile3, Relative_Prevalence_of_Most_Common_Rhythmic_Values, Difference_Between_Most_Common_Rhythmic_Values, Dominant_Seventh_Chords, Direction_of_Melodic_Motion, F0env_sma_linregerrQ))
outcome <- mean_df$A_mean

ctrl <- gafsControl(functions = caretGA)
obj.test.100.A <- gafs(x = predictors, 
            y = outcome,
            iters = 100,
            gafsControl = ctrl,
            method = "lm")
```


```{r}
obj.test.100.A
```


Initial model with the selected predictors from the Genetic Algorithm

```{r GA_Model_multiple_regression_arousal}
library(lmerTest)
model.A_GA <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + pcm_zcr_sma_skewness + Similar_Motion + (1 |Song2) + (1 |ID), data=all_features)
res <- summary(model.A_GA)
res
model.A_GA.AIC <- AIC(model.A_GA)
model.A_GA.AIC
```

Updated model by dropping not relevant predictors

```{r GA_Model_multiple_regression_arousal2}
model.A_GA <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + pcm_zcr_sma_skewness + (1 |Song2) + (1 |ID), data=all_features)
res <- summary(model.A_GA)
res
model.A_GA.AIC <- AIC(model.A_GA)
model.A_GA.AIC
```


##########################################
            FORWARD SELECTION  
##########################################

Search for adding a predictor that reduces AIC of Model.1

```{r forward_selection_Arousal}
df <- subset(all_features, select=-c(ID, Song, Category, Song2, Arousal, Valence)) 
all_vars <- colnames(df)

GA.rel_Arousal1 <- data.frame(A="Most_Common_Rhythmic_Value", B="Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized", C="pcm_zcr_sma_skewness", AIC = 2613.794)
GA_rel_Arousal.OPT <- data.frame(A = character(), B = character(), C = character(), D = character(), AIC = numeric())

for (i in 1:nrow(GA.rel_Arousal1)) {
  x <- as.vector(t(GA.rel_Arousal1[i,]))
  for (var in all_vars){
    if (var != "Arousal" & var != "Valence" & var != x[1] & var != x[2] & var != x[3]){
      A.formula <- as.formula(paste("Arousal ~", paste(c(x[1], x[2], x[3], var), collapse= " + "),"+ (1 |Song2) + (1 |ID)"))
      model.A <- lmer(formula=A.formula, data=all_features)
      res <- summary(model.A)
      if (AIC(model.A)<=x[4]){
        new_row <- data.frame(x[1], x[2], x[3], var, AIC(model.A))
        names(new_row) <- c("A", "B", "C", "D", "AIC")
        GA_rel_Arousal.OPT <- rbind(new_row, GA_rel_Arousal.OPT)
      }
    }
  }
}
GA_rel_Arousal.OPT
```

We inspect the results of the new model (Model.2)

```{r GA_Model2_multiple_regression_arousal}
model.A_GA.2 <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + pcm_zcr_sma_skewness + F0env_sma_linregerrQ + (1 |Song2) + (1 |ID), data=all_features)
res <- summary(model.A_GA.2)
res
model.A_GA.2.AIC <- AIC(model.A_GA.2)
model.A_GA.2.AIC
```

Search for adding a predictor that reduces AIC of Model.2

```{r forward_selection_Arousal.2}
df <- subset(all_features, select=-c(ID, Song, Category, Song2, Arousal, Valence)) 
all_vars <- colnames(df)

GA.rel_Arousal1 <- data.frame(A="Most_Common_Rhythmic_Value", B="Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized", C="pcm_zcr_sma_skewness", D="F0env_sma_linregerrQ", AIC = 2613.573)
GA_rel_Arousal.OPT <- data.frame(A = character(), B = character(), C = character(), D = character(), E = character(), AIC = numeric())

for (i in 1:nrow(GA.rel_Arousal1)) {
  x <- as.vector(t(GA.rel_Arousal1[i,]))
  for (var in all_vars){
    if (var != "Arousal" & var != "Valence" & var != x[1] & var != x[2] & var != x[3] & var != x[4]){
      A.formula <- as.formula(paste("Arousal ~", paste(c(x[1], x[2], x[3], x[4], var), collapse= " + "),"+ (1 |Song2) + (1 |ID)"))
      model.A <- lmer(formula=A.formula, data=all_features)
      res <- summary(model.A)
      if (AIC(model.A)<=x[5]){
        new_row <- data.frame(x[1], x[2], x[3], x[4], var, AIC(model.A))
        names(new_row) <- c("A", "B", "C", "D", "E", "AIC")
        GA_rel_Arousal.OPT <- rbind(new_row, GA_rel_Arousal.OPT)
      }
    }
  }
}
GA_rel_Arousal.OPT
```

We inspect the results of the new model (Model.3)

```{r GA_Model3_multiple_regression_arousal}
model.A_GA.2 <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + pcm_zcr_sma_skewness + F0env_sma_linregerrQ + Median_Rhythmic_Value_Offset + (1 |Song2) + (1 |ID), data=all_features)
res <- summary(model.A_GA.2)
res
model.A_GA.2.AIC <- AIC(model.A_GA.2)
model.A_GA.2.AIC
```


Search for adding a predictor that reduces AIC of Model.3

```{r forward_selection_Arousal.3}
df <- subset(all_features, select=-c(ID, Song, Category, Song2, Arousal, Valence)) 
all_vars <- colnames(df)

GA.rel_Arousal2 <- data.frame(A="Most_Common_Rhythmic_Value", B="Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized", C="pcm_zcr_sma_skewness", D="F0env_sma_linregerrQ", E="Median_Rhythmic_Value_Offset", AIC = 2610.255)
GA_rel_Arousal.OPT2 <- data.frame(A = character(), B = character(), C = character(), D = character(), E = character(), G = character(), AIC = numeric())

for (i in 1:nrow(GA.rel_Arousal2)) {
  x <- as.vector(t(GA.rel_Arousal2[i,]))
  for (var in all_vars){
    if (var != "Arousal" & var != "Valence" & var != x[1] & var != x[2] & var != x[3] & var != x[4] & var != x[5]){
      A.formula <- as.formula(paste("Arousal ~", paste(c(x[1], x[2], x[3], x[4], x[5], var), collapse= " + "),"+ (1 |Song2) + (1 |ID)"))
      model.A <- lmer(formula=A.formula, data=all_features)
      res <- summary(model.A)
      if (AIC(model.A)<=x[6]){
        new_row <- data.frame(x[1], x[2], x[3], x[4], x[5], var, AIC(model.A))
        names(new_row) <- c("A", "B", "C", "D", "E", "G", "AIC")
        GA_rel_Arousal.OPT2 <- rbind(new_row, GA_rel_Arousal.OPT2)
      }
    }
  }
}
GA_rel_Arousal.OPT2
```


We inspect the results of the new model (Model.4)

```{r GA_Model4_multiple_regression_arousal}
model.A_GA.3 <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + pcm_zcr_sma_skewness + F0env_sma_linregerrQ + Median_Rhythmic_Value_Offset + pcm_zcr_sma_stddev + (1 |Song2) + (1 |ID), data=all_features)
res <- summary(model.A_GA.3)
res
model.A_GA.3.AIC <- AIC(model.A_GA.3)
model.A_GA.3.AIC
```


Search for adding a predictor that reduces AIC of Model.4

```{r forward_selection_Arousal.4}
df <- subset(all_features, select=-c(ID, Song, Category, Song2, Arousal, Valence)) 
all_vars <- colnames(df)

GA.rel_Arousal3 <- data.frame(A="Most_Common_Rhythmic_Value", B="Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized", C="pcm_zcr_sma_skewness", D="F0env_sma_linregerrQ", E="Median_Rhythmic_Value_Offset", G="pcm_zcr_sma_stddev", AIC = 2607.502)
GA_rel_Arousal.OPT3 <- data.frame(A = character(), B = character(), C = character(), D = character(), E = character(), G = character(), H = character(), AIC = numeric())

for (i in 1:nrow(GA.rel_Arousal3)) {
  x <- as.vector(t(GA.rel_Arousal3[i,]))
  for (var in all_vars){
    if (var != "Arousal" & var != "Valence" & var != x[1] & var != x[2] & var != x[3] & var != x[4] & var != x[5] & var != x[6]){
      A.formula <- as.formula(paste("Arousal ~", paste(c(x[1], x[2], x[3], x[4], x[5], x[6], var), collapse= " + "),"+ (1 |Song2) + (1 |ID)"))
      model.A <- lmer(formula=A.formula, data=all_features)
      res <- summary(model.A)
      if (AIC(model.A)<=x[7]){
        new_row <- data.frame(x[1], x[2], x[3], x[4], x[5], x[6], var, AIC(model.A))
        names(new_row) <- c("A", "B", "C", "D", "E", "G", "H", "AIC")
        GA_rel_Arousal.OPT3 <- rbind(new_row, GA_rel_Arousal.OPT3)
      }
    }
  }
}
GA_rel_Arousal.OPT3
```


Search for adding two predictors that reduces AIC of Model.4

```{r forward_selection_Arousal.3}
df <- subset(all_features, select=-c(ID, Song, Category, Song2, Arousal, Valence)) 
all_vars <- colnames(df)

GA.rel_Arousal4 <- data.frame(A="Most_Common_Rhythmic_Value", B="Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized", C="pcm_zcr_sma_skewness", D="F0env_sma_linregerrQ", E="Median_Rhythmic_Value_Offset", G="pcm_zcr_sma_stddev", AIC = 2607.502)
GA_rel_Arousal.OPT4 <- data.frame(A = character(), B = character(), C = character(), D = character(), E = character(), G = character(), H = character(), I = character(), AIC = numeric())

for (i in 1:nrow(GA.rel_Arousal4)) {
  x <- as.vector(t(GA.rel_Arousal4[i,]))
  for (var in all_vars){
    if (var != "Arousal" & var != "Valence" & var != x[1] & var != x[2] & var != x[3] & var != x[4] & var != x[5] & var != x[6]){
      for (var2 in all_vars){
        if (var2 != "Arousal" & var2 != "Valence" & var2 != x[1] & var2 != x[2] & var2 != x[3] & var != x[4] & var != x[5] & var != x[6] & var2 != var){
          A.formula <- as.formula(paste("Arousal ~", paste(c(x[1], x[2], x[3], x[4], x[5], x[6], var, var2), collapse= " + "),"+ (1 |Song2) + (1 |ID)"))
          model.A <- lmer(formula=A.formula, data=all_features)
          res <- summary(model.A)
          if (AIC(model.A)<=x[7]){
            new_row <- data.frame(x[1], x[2], x[3], x[4], x[5], x[6], var, var2, AIC(model.A))
            names(new_row) <- c("A", "B", "C", "D", "E", "G", "H", "I", "AIC")
            GA_rel_Arousal.OPT4 <- rbind(new_row, GA_rel_Arousal.OPT4)
          }
        }
      }
    }
  }
}
GA_rel_Arousal.OPT4
```


```{r Best.Model.Arousal}
Best.Model.A <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + pcm_zcr_sma_skewness + F0env_sma_linregerrQ + Median_Rhythmic_Value_Offset + pcm_zcr_sma_stddev + (1 |Song2) + (1 |ID), data=all_features)
res <- summary(Best.Model.A)
res
Best.Model.A.AIC <- AIC(Best.Model.A)
Best.Model.A.AIC
```


----------------------------------------------------------------------------------------------------------------------------------------------------------
--------------------------------------------------------------------FEATURE SELECTION VALENCE-------------------------------------------------------------
----------------------------------------------------------------------------------------------------------------------------------------------------------

  ##########################################
             GENETIC ALGORITHM  
  ##########################################
  
Initialise predictors search with the feature showing a correlation with the outcome variable (Valence) higher than 0.3

```{r GA_feature_selection_VALENCE}
library(caret)

set.seed(10)
predictors <- subset(mean_df, select=c(F0env_sma_quartile3, Minor_Major_Triad_Ratio,	Minor_Major_Melodic_Third_Ratio, F0env_sma_skewness,	pcm_intensity_sma_minPos,	Similar_Motion,	Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized, Diminished_and_Augmented_Triads,	Dynamic_Range, Non.Standard_Chords, pcm_zcr_sma_skewness, Vertical_Perfect_Fifths, Vertical_Minor_Seconds, Amount_of_Staccato, Prevalence_of_Very_Long_Rhythmic_Values, Prevalence_of_Second_Most_Common_Vertical_Interval, Importance_of_Bass_Register, F0env_sma_max, F0_sma_maxPos, Melodic_Large_Intervals, Vertical_Sixths))
outcome <- mean_df$V_mean

ctrl <- gafsControl(functions = caretGA)
obj.test.100 <- gafs(x = predictors, 
            y = outcome,
            iters = 100,
            gafsControl = ctrl,
            method = "lm")
```


```{r obj.100}
obj.test.100
```


Initial model with the selected predictors from the Genetial Algorithm

```{r GA_Model_multiple_regression_valence}
model.V_GA <- lmer(Valence ~ Minor_Major_Triad_Ratio + F0env_sma_skewness + Dynamic_Range + pcm_zcr_sma_skewness + Vertical_Sixths + (1 |Song2) + (1 |ID), data=all_features)
res <- summary(model.V_GA)
res
model.V_GA.AIC <- AIC(model.V_GA)
model.V_GA.AIC
```

Updated model by dropping not relevant predictors

```{r GA_Model_multiple_regression_valence2}
model.V_GA <- lmer(Valence ~ Minor_Major_Triad_Ratio + F0env_sma_skewness + pcm_zcr_sma_skewness + (1 |Song2) + (1 |ID), data=all_features)
res <- summary(model.V_GA)
res
model.V_GA.AIC <- AIC(model.V_GA)
model.V_GA.AIC
```

##########################################
            FORWARD SELECTION  
##########################################

Search for adding a predictor that reduces AIC of Model.1

```{r forward_selection_Valence}
df <- subset(all_features, select=-c(ID, Song, Category, Song2, Arousal, Valence)) 
all_vars <- colnames(df)

GA.rel_Valence1 <- data.frame(A="Minor_Major_Triad_Ratio", B="F0env_sma_skewness", C="pcm_zcr_sma_skewness", AIC = 2511.897)
GA_rel_Valence.OPT <- data.frame(A = character(), B = character(), C = character(), D = character(), AIC = numeric())

for (i in 1:nrow(GA.rel_Valence1)) {
  x <- as.vector(t(GA.rel_Valence1[i,]))
  for (var in all_vars){
    if (var != "Arousal" & var != "Valence" & var != x[1] & var != x[2] & var != x[3]){
      V.formula <- as.formula(paste("Valence ~", paste(c(x[1], x[2], x[3], var), collapse= " + "),"+ (1 |Song2) + (1 |ID)"))
      model.V <- lmer(formula=V.formula, data=all_features)
      res <- summary(model.V)
      if (AIC(model.V)<=x[4]){
        new_row <- data.frame(x[1], x[2], x[3], var, AIC(model.V))
        names(new_row) <- c("A", "B", "C", "D", "AIC")
        GA_rel_Valence.OPT <- rbind(new_row, GA_rel_Valence.OPT)
      }
    }
  }
}
GA_rel_Valence.OPT
```

We inspect the results of the new model (Model.2)

```{r GA_Model2_multiple_regression_valence}
model.V_GA.2 <- lmer(Valence ~ Minor_Major_Triad_Ratio + F0env_sma_skewness + pcm_zcr_sma_skewness + BPM + (1 |Song2) + (1 |ID), data=all_features)
res <- summary(model.V_GA.2)
res
model.V_GA.2.AIC <- AIC(model.V_GA.2)
model.V_GA.2.AIC
```


Search for adding a predictor that reduces AIC of Model.2

```{r forward_selection_Valence2}
df <- subset(all_features, select=-c(ID, Song, Category, Song2, Arousal, Valence)) 
all_vars <- colnames(df)

GA.rel_Valence1 <- data.frame(A="Minor_Major_Triad_Ratio", B="F0env_sma_skewness", C="pcm_zcr_sma_skewness", D="BPM", AIC = 2510.653)
GA_rel_Valence.OPT <- data.frame(A = character(), B = character(), C = character(), D = character(), E = character(), AIC = numeric())

for (i in 1:nrow(GA.rel_Valence1)) {
  x <- as.vector(t(GA.rel_Valence1[i,]))
  for (var in all_vars){
    if (var != "Arousal" & var != "Valence" & var != x[1] & var != x[2] & var != x[3] & var != x[4]){
      V.formula <- as.formula(paste("Valence ~", paste(c(x[1], x[2], x[3], x[4], var), collapse= " + "),"+ (1 |Song2) + (1 |ID)"))
      model.V <- lmer(formula=V.formula, data=all_features)
      res <- summary(model.V)
      if (AIC(model.V)<=x[5]){
        new_row <- data.frame(x[1], x[2], x[3], x[4], var, AIC(model.V))
        names(new_row) <- c("A", "B", "C", "D", "E", "AIC")
        GA_rel_Valence.OPT <- rbind(new_row, GA_rel_Valence.OPT)
      }
    }
  }
}
GA_rel_Valence.OPT
```

We inspect the results of the new model (Model.3)

```{r GA_Model2_multiple_regression_valence}
model.V_GA.3 <- lmer(Valence ~ Minor_Major_Triad_Ratio + F0env_sma_skewness + pcm_zcr_sma_skewness + BPM + Amount_of_Staccato + (1 |Song2) + (1 |ID), data=all_features)
res <- summary(model.V_GA.3)
res
model.V_GA.3.AIC <- AIC(model.V_GA.3)
model.V_GA.3.AIC
```


Search for adding a predictor that reduces AIC of Model.3

```{r forward_selection_Valence3}
df <- subset(all_features, select=-c(ID, Song, Category, Song2, Arousal, Valence)) 
all_vars <- colnames(df)

GA.rel_Valence1 <- data.frame(A="Minor_Major_Triad_Ratio", B="F0env_sma_skewness", C="pcm_zcr_sma_skewness", D="BPM", E="Amount_of_Staccato", AIC = 2510.505)
GA_rel_Valence.OPT <- data.frame(A = character(), B = character(), C = character(), D = character(), E = character(), G = character(), AIC = numeric())

for (i in 1:nrow(GA.rel_Valence1)) {
  x <- as.vector(t(GA.rel_Valence1[i,]))
  for (var in all_vars){
    if (var != "Arousal" & var != "Valence" & var != x[1] & var != x[2] & var != x[3] & var != x[4] & var != x[5]){
      V.formula <- as.formula(paste("Valence ~", paste(c(x[1], x[2], x[3], x[4], x[5], var), collapse= " + "),"+ (1 |Song2) + (1 |ID)"))
      model.V <- lmer(formula=V.formula, data=all_features)
      res <- summary(model.V)
      if (AIC(model.V)<=x[6]){
        new_row <- data.frame(x[1], x[2], x[3], x[4], x[5], var, AIC(model.V))
        names(new_row) <- c("A", "B", "C", "D", "E", "G", "AIC")
        GA_rel_Valence.OPT <- rbind(new_row, GA_rel_Valence.OPT)
      }
    }
  }
}
GA_rel_Valence.OPT
```

We inspect the results of the new model (Model.4)

```{r GA_Model2_multiple_regression_valence}
model.V_GA.4 <- lmer(Valence ~ Minor_Major_Triad_Ratio + F0env_sma_skewness + pcm_zcr_sma_skewness + BPM + Amount_of_Staccato + F0env_sma_linregerrQ + (1 |Song2) + (1 |ID), data=all_features)
res <- summary(model.V_GA.4)
res
model.V_GA.4.AIC <- AIC(model.V_GA.4)
model.V_GA.4.AIC
```


Search for adding a predictor that reduces AIC of Model.4

```{r forward_selection_Valence4}
df <- subset(all_features, select=-c(ID, Song, Category, Song2, Arousal, Valence)) 
all_vars <- colnames(df)

GA.rel_Valence1 <- data.frame(A="Minor_Major_Triad_Ratio", B="F0env_sma_skewness", C="pcm_zcr_sma_skewness", D="BPM", E="Amount_of_Staccato", G="F0env_sma_linregerrQ", AIC = 2507.345)
GA_rel_Valence.OPT <- data.frame(A = character(), B = character(), C = character(), D = character(), E = character(), G = character(), H = character(), AIC = numeric())

for (i in 1:nrow(GA.rel_Valence1)) {
  x <- as.vector(t(GA.rel_Valence1[i,]))
  for (var in all_vars){
    if (var != "Arousal" & var != "Valence" & var != x[1] & var != x[2] & var != x[3] & var != x[4] & var != x[5] & var != x[6]){
      V.formula <- as.formula(paste("Valence ~", paste(c(x[1], x[2], x[3], x[4], x[5], x[6], var), collapse= " + "),"+ (1 |Song2) + (1 |ID)"))
      model.V <- lmer(formula=V.formula, data=all_features)
      res <- summary(model.V)
      if (AIC(model.V)<=x[7]){
        new_row <- data.frame(x[1], x[2], x[3], x[4], x[5], x[6], var, AIC(model.V))
        names(new_row) <- c("A", "B", "C", "D", "E", "G", "H", "AIC")
        GA_rel_Valence.OPT <- rbind(new_row, GA_rel_Valence.OPT)
      }
    }
  }
}
GA_rel_Valence.OPT
```

We inspect the results of the new model (Model.5)

```{r GA_Model2_multiple_regression_valence}
model.V_GA.5 <- lmer(Valence ~ Minor_Major_Triad_Ratio + F0env_sma_skewness + pcm_zcr_sma_skewness + BPM + Amount_of_Staccato + F0env_sma_linregerrQ + Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized + (1 |Song2) + (1 |ID), data=all_features)
res <- summary(model.V_GA.5)
res
model.V_GA.5.AIC <- AIC(model.V_GA.5)
model.V_GA.5.AIC
```


Search for adding a predictor that reduces AIC of Model.5

```{r forward_selection_Valence5}
df <- subset(all_features, select=-c(ID, Song, Category, Song2, Arousal, Valence)) 
all_vars <- colnames(df)

GA.rel_Valence1 <- data.frame(A="Minor_Major_Triad_Ratio", B="F0env_sma_skewness", C="pcm_zcr_sma_skewness", D="BPM", E="Amount_of_Staccato", G="F0env_sma_linregerrQ", H="Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized", IC = 2507.314)
GA_rel_Valence.OPT <- data.frame(A = character(), B = character(), C = character(), D = character(), E = character(), G = character(), H = character(), I = character(), AIC = numeric())

for (i in 1:nrow(GA.rel_Valence1)) {
  x <- as.vector(t(GA.rel_Valence1[i,]))
  for (var in all_vars){
    if (var != "Arousal" & var != "Valence" & var != x[1] & var != x[2] & var != x[3] & var != x[4] & var != x[5] & var != x[6] & var != x[7]){
      V.formula <- as.formula(paste("Valence ~", paste(c(x[1], x[2], x[3], x[4], x[5], x[6], x[7], var), collapse= " + "),"+ (1 |Song2) + (1 |ID)"))
      model.V <- lmer(formula=V.formula, data=all_features)
      res <- summary(model.V)
      if (AIC(model.V)<=x[8]){
        new_row <- data.frame(x[1], x[2], x[3], x[4], x[5], x[6], x[7], var, AIC(model.V))
        names(new_row) <- c("A", "B", "C", "D", "E", "G", "H", "I", "AIC")
        GA_rel_Valence.OPT <- rbind(new_row, GA_rel_Valence.OPT)
      }
    }
  }
}
GA_rel_Valence.OPT
```


```{r Best.Model.Valence}
Best.Model.V <- lmer(Valence ~ Minor_Major_Triad_Ratio + F0env_sma_skewness + pcm_zcr_sma_skewness + BPM + Amount_of_Staccato + F0env_sma_linregerrQ + Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized + (1 |Song2) + (1 |ID), data=all_features)
res <- summary(Best.Model.V)
res
Best.Model.V.AIC <- AIC(Best.Model.V)
Best.Model.V.AIC
```



----------------------------------------------------------------------------------------------------------------------------------------------------------
--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
          CATEGORICAL ASSESSMENT    CATEGORICAL ASSESSMENT    CATEGORICAL ASSESSMENT    CATEGORICAL ASSESSMENT    CATEGORICAL ASSESSMENT
----------------------------------------------------------------------------------------------------------------------------------------------------------
--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------


```{r lme_selected_features_amazement}
library(nlme)
library(lme4)
amazement <- all_features[which(all_features$Category == "Amazement"),]

amazement.Model.A <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + pcm_zcr_sma_skewness + F0env_sma_linregerrQ + Median_Rhythmic_Value_Offset + pcm_zcr_sma_stddev + (1 |Song2) + (1 |ID), data=amazement)
res <- summary(amazement.Model.A)
res
amazement.Model.A.AIC <- AIC(amazement.Model.A)
amazement.Model.A.AIC

amazement.Model.V <- lmer(Valence ~ Minor_Major_Triad_Ratio + F0env_sma_skewness + pcm_zcr_sma_skewness + BPM + Amount_of_Staccato + F0env_sma_linregerrQ + Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized + (1 |Song2) + (1 |ID), data=amazement)
res <- summary(amazement.Model.V)
res
amazement.Model.V.AIC <- AIC(amazement.Model.V)
amazement.Model.V.AIC
```


```{r lme_selected_features_joy}
Joy <- all_features[which(all_features$Category == "Joy"),]

Joy.Model.A <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + Median_Rhythmic_Value_Offset + pcm_zcr_sma_skewness + pcm_zcr_sma_stddev + F0env_sma_linregerrQ + (1 |Song2) + (1 |ID), data=Joy)
res <- summary(Joy.Model.A)
res
Joy.Model.A.AIC <- AIC(Joy.Model.A)
Joy.Model.A.AIC

Joy.Model.V <- lmer(Valence ~ Minor_Major_Triad_Ratio + pcm_zcr_sma_skewness + F0env_sma_skewness + F0env_sma_linregerrQ + Amount_of_Staccato + Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized + BPM + (1 |Song2) + (1 |ID), data=Joy)
res <- summary(Joy.Model.V)
res
Joy.Model.V.AIC <- AIC(Joy.Model.V)
Joy.Model.V.AIC
```


```{r lme_selected_features_activation}
Activation <- all_features[which(all_features$Category == "Activation"),]

Activation.Model.A <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + Median_Rhythmic_Value_Offset + pcm_zcr_sma_skewness + pcm_zcr_sma_stddev + F0env_sma_linregerrQ + (1 |Song2) + (1 |ID), data=Activation)
res <- summary(Activation.Model.A)
res
Activation.Model.A.AIC <- AIC(Activation.Model.A)
Activation.Model.A.AIC

Activation.Model.V <- lmer(Valence ~ Minor_Major_Triad_Ratio + pcm_zcr_sma_skewness + F0env_sma_skewness + F0env_sma_linregerrQ + Amount_of_Staccato + Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized + BPM + (1 |Song2) + (1 |ID), data=Activation)
res <- summary(Activation.Model.V)
res
Activation.Model.V.AIC <- AIC(Activation.Model.V)
Activation.Model.V.AIC
```


```{r lme_selected_features_dysphoria}
Dysphoria <- all_features[which(all_features$Category == "Dysphoria"),]

Dysphoria.Model.A <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + Median_Rhythmic_Value_Offset + pcm_zcr_sma_skewness + pcm_zcr_sma_stddev + F0env_sma_linregerrQ + (1 |Song2) + (1 |ID), data=Dysphoria)
res <- summary(Dysphoria.Model.A)
res
Dysphoria.Model.A.AIC <- AIC(Dysphoria.Model.A)
Dysphoria.Model.A.AIC

Dysphoria.Model.V <- lmer(Valence ~ Minor_Major_Triad_Ratio + pcm_zcr_sma_skewness + F0env_sma_skewness + F0env_sma_linregerrQ + Amount_of_Staccato + Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized + BPM + (1 |Song2) + (1 |ID), data=Dysphoria)
res <- summary(Dysphoria.Model.V)
res
Dysphoria.Model.V.AIC <- AIC(Dysphoria.Model.V)
Dysphoria.Model.V.AIC
```


```{r lme_selected_features_power}
Power <- all_features[which(all_features$Category == "Power"),]

Power.Model.A <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + pcm_zcr_sma_skewness + F0env_sma_linregerrQ + Median_Rhythmic_Value_Offset + pcm_zcr_sma_stddev + (1 |Song2) + (1 |ID), data=Power)
res <- summary(Power.Model.A)
res
Power.Model.A.AIC <- AIC(Power.Model.A)
Power.Model.A.AIC

Power.Model.V <- lmer(Valence ~ Minor_Major_Triad_Ratio + F0env_sma_skewness + pcm_zcr_sma_skewness + BPM + Amount_of_Staccato + F0env_sma_linregerrQ + Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized + (1 |Song2) + (1 |ID), data=Power)
res <- summary(Power.Model.V)
res
Power.Model.V.AIC <- AIC(Power.Model.V)
Power.Model.V.AIC
```


```{r lme_selected_features_sadness}
Sadness <- all_features[which(all_features$Category == "Sadness"),]

Sadness.Model.A <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + pcm_zcr_sma_skewness + F0env_sma_linregerrQ + Median_Rhythmic_Value_Offset + pcm_zcr_sma_stddev + (1 |Song2) + (1 |ID), data=Sadness)
res <- summary(Sadness.Model.A)
res
Sadness.Model.A.AIC <- AIC(Sadness.Model.A)
Sadness.Model.A.AIC

Sadness.Model.V <- lmer(Valence ~ Minor_Major_Triad_Ratio + F0env_sma_skewness + pcm_zcr_sma_skewness + BPM + Amount_of_Staccato + F0env_sma_linregerrQ + Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized + (1 |Song2) + (1 |ID), data=Sadness)
res <- summary(Sadness.Model.V)
res
Sadness.Model.V.AIC <- AIC(Sadness.Model.V)
Sadness.Model.V.AIC
```


```{r lme_selected_features_sensuality}
Sensuality <- all_features[which(all_features$Category == "Sensuality"),]

Sensuality.Model.A <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + pcm_zcr_sma_skewness + F0env_sma_linregerrQ + Median_Rhythmic_Value_Offset + pcm_zcr_sma_stddev + (1 |Song2) + (1 |ID), data=Sensuality)
res <- summary(Sensuality.Model.A)
res
Sensuality.Model.A.AIC <- AIC(Sensuality.Model.A)
Sensuality.Model.A.AIC

Sensuality.Model.V <- lmer(Valence ~ Minor_Major_Triad_Ratio + F0env_sma_skewness + pcm_zcr_sma_skewness + BPM + Amount_of_Staccato + F0env_sma_linregerrQ + Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized + (1 |Song2) + (1 |ID), data=Sensuality)
res <- summary(Sensuality.Model.V)
res
Sensuality.Model.V.AIC <- AIC(Sensuality.Model.V)
Sensuality.Model.V.AIC
```


```{r lme_selected_features_TenderLonging}
TenderLonging <- all_features[which(all_features$Category == "TenderLonging"),]

TenderLonging.Model.A <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + pcm_zcr_sma_skewness + F0env_sma_linregerrQ + Median_Rhythmic_Value_Offset + pcm_zcr_sma_stddev + (1 |Song2) + (1 |ID), data=TenderLonging)
res <- summary(TenderLonging.Model.A)
res
TenderLonging.Model.A.AIC <- AIC(TenderLonging.Model.A)
TenderLonging.Model.A.AIC

TenderLonging.Model.V <- lmer(Valence ~ Minor_Major_Triad_Ratio + F0env_sma_skewness + pcm_zcr_sma_skewness + BPM + Amount_of_Staccato + F0env_sma_linregerrQ + Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized + (1 |Song2) + (1 |ID), data=TenderLonging)
res <- summary(TenderLonging.Model.V)
res
TenderLonging.Model.V.AIC <- AIC(TenderLonging.Model.V)
TenderLonging.Model.V.AIC
```


```{r lme_selected_features_Tranquility}
Tranquility <- all_features[which(all_features$Category == "Tranquility"),]

Tranquility.Model.A <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + Median_Rhythmic_Value_Offset + pcm_zcr_sma_skewness + pcm_zcr_sma_stddev + F0env_sma_linregerrQ + (1 |Song2) + (1 |ID), data=Tranquility)
res <- summary(Tranquility.Model.A)
res
Tranquility.Model.A.AIC <- AIC(Tranquility.Model.A)
Tranquility.Model.A.AIC

Tranquility.Model.V <- lmer(Valence ~ Minor_Major_Triad_Ratio + pcm_zcr_sma_skewness + F0env_sma_skewness + F0env_sma_linregerrQ + Amount_of_Staccato + Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized + BPM + (1 |Song2) + (1 |ID), data=Tranquility)
res <- summary(Tranquility.Model.V)
res
Tranquility.Model.V.AIC <- AIC(Tranquility.Model.V)
Tranquility.Model.V.AIC
```


```{r lme_selected_features_Transcendence}
Transcendence <- all_features[which(all_features$Category == "Transcendence"),]

Transcendence.Model.A <- lmer(Arousal ~ Most_Common_Rhythmic_Value + Number_of_Strong_Rhythmic_Pulses_._Tempo_Standardized + pcm_zcr_sma_skewness + F0env_sma_linregerrQ + Median_Rhythmic_Value_Offset + pcm_zcr_sma_stddev + (1 |Song2) + (1 |ID), data=Transcendence)
res <- summary(Transcendence.Model.A)
res
Transcendence.Model.A.AIC <- AIC(Transcendence.Model.A)
Transcendence.Model.A.AIC

Transcendence.Model.V <- lmer(Valence ~ Minor_Major_Triad_Ratio + F0env_sma_skewness + pcm_zcr_sma_skewness + BPM + Amount_of_Staccato + F0env_sma_linregerrQ + Strength_Ratio_of_Two_Strongest_Rhythmic_Pulses_._Tempo_Standardized + (1 |Song2) + (1 |ID), data=Transcendence)
res <- summary(Transcendence.Model.V)
res
Transcendence.Model.V.AIC <- AIC(Transcendence.Model.V)
Transcendence.Model.V.AIC
```
